### 2012-05-11 inst/examples/value_of_information.Rmd
value of information
snowfall only once

`ro cache=TRUE, tidy=FALSE, warning=FALSE, comment=NA, message=FALSE, refresh=2 fig.width=10, fig.height=10 or`

@@

>>>>

`ro cache=TRUE, tidy=FALSE, warning=FALSE, comment=NA, message=FALSE, fig.width=10, fig.height=10 or`

@@

``` {r }
SDP_Mat <- SDP_by_simulation(f, pars, x_grid, h_grid, z_g, z_m, z_i, reps=999)
````
